Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-05-18 PAPER.tex
added text saying we normalize the final posterior
edited caption to fig 18

Finally, our transfer functions are shown in Figure \ref{fig:sigloss_transfercurve} for both the weighted (left) and unweighted (right) cases. Our bootstrapped power spectrum outputs are shown as black points and the colored heat-map overlaid on top is the likelihood function modified by our prior. Although we only show figures for one $k$-value, we note that 
the shape of the transfer curve is similar for all $k$'s. We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|\widehat{P}_{\rm out})$ where we recall that $\widehat{P}_{\rm out}$ is a model of our data. To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$), shown by the gray solid line, to yield a posterior distribution for the signal. We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.pdf}
	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $\widehat{P}_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}. Power spectra values (black points) are generated for $20$ realizations of $\textbf{e}$ per signal injection level. Kernel density estimations of the power spectrum transfer functions are shown as colored 
heat-maps on top of the points for the cases of empirically estimated inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{P}}_{x}$, from which a posterior distribution for the signal is extracted. From these plots, it is clear that the weighted case results in $\sim4$ orders of magnitude of signal loss at the data-only power spectrum value, whereas the uniform-weighted case does 
not exhibit loss. The general shape of these transfer functions are also shown by the black curves in Figure \ref{fig:sigloss_terms} for comparison.}
	\label{fig:sigloss_transfercurve}
\end{figure*}

>>>>

Finally, our transfer functions are shown in Figure \ref{fig:sigloss_transfercurve} for both the weighted (left) and unweighted (right) cases. Our bootstrapped power spectrum outputs are shown as black points and the colored heat-map overlaid on top is the likelihood function modified by our prior. Although we only show figures for one $k$-value, we note that 
the shape of the transfer curve is similar for all $k$'s. We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|\widehat{P}_{\rm out})$ where we recall that $\widehat{P}_{\rm out}$ is a model of our data. To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$), shown by the gray solid line, to yield a posterior distribution for the signal. We normalize this final distribution and compute the $95\%$ confidence interval (an upper limit on EoR).

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.pdf}
	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $\widehat{P}_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}. Power spectra values (black points) are generated for $20$ realizations of $\textbf{e}$ per signal injection level. Assuming our $\widehat{P}_{\rm out}$ values sample a Gaussian distribution, we fit Gaussians to each injection level based on the mean and variance of the simulation outputs. This entire likelihood function is then multiplied by a Jeffreys prior for $p(P_{\rm in}$), with the final result shown as the colored 
heat-maps on top of the points. Two cases are displayed: empirically estimated inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{P}}_{x}$, from which a posterior distribution for the signal is extracted. From these plots, it is clear that the weighted case results in $\sim4$ orders of magnitude of signal loss at the data-only power spectrum value, whereas the uniform-weighted case does 
not exhibit loss. The general shape of these transfer functions are also shown by the black curves in Figure \ref{fig:sigloss_terms} for comparison.}
	\label{fig:sigloss_transfercurve}
\end{figure*}
